Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-07-30 documentation/paper.tex
Added brief description of methods

\documentclass[12pt]{article}
\begin{document}
\title{Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector}
\author{Brendon Matusch}
\date{\today}
\maketitle
\end{document}

>>>>

\documentclass[12pt]{article}

% Use 1-inch margins even though the font is 12-point
\usepackage[margin=1in]{geometry}
\usepackage{textgreek}

\begin{document}

% A description of the various techniques used to discriminate between neutrons and alphas
\section{Methods}

Two key techniques have been used for the task of discrimination between neutrons/WIMP candidates and alpha particles in the PICO-60 bubble chamber. The first, Acoustic Parameter (AP), is a function of the 8-band Fourier transform \textbeta \textsubscript{8}. It makes use of the increased resonant energy in certain frequency bands, relative to neutrons, present in the majority of alpha particles. The second, Deep Learning (DL) consists of a wide variety of neural networks, which are trained on either the raw waveform \textomega{}, the arbitrary-resolution Fourier transform \textbeta \textsubscript{N}, or the image \textiota.

% A section about AP, how it works, and its limitations
\subsection{Acoustic Parameter}
Placeholder

\end{document}
